\Large \bf Cyclone: Warp Speed Replication for Key Value Stores

### 2017-04-21 paper/paper.tex
More updates to paper.

@@

>>>>

\begin{figure}
\centering
\includegraphics[scale=0.6]{results2/problem.pdf}
\caption{Rocksdb Write Ahead Logging Impact}
\label{fig:wal_impact}
\end{figure}

@@

The assumption in Figure~\ref{fig:ganged_ops} is that each ganged operation is
mapped to a unique barrier. We achieve this by using a fixed piece memory owned
by the leader core to hold the barrier and write the nonce to it in order to
indicate that the barrer is active. Non-leader cores watch for the nonce to know
when to execute the ganged operation barrier in Figure~\ref{fig:ganged_ops},
while also monitoring the leader's published view to detect the case where the
ganged operation fails to replicate on the leader's physical log.

Finally, we describe how we generate the nonce. The nonce is generated on the
injector core by concatenating the ethernet MAC ID of the first NIC on the
system with a 64 bit value that is the number of CPU timestamp counter cycles
since epoch time (read from the real time clock at startup plus the number of
cycles from the CPU {\tt rdtsc} instruction). The nonce can only be repeated if
the same machine manages to fail and come back up in less time than the real
time clock drift (controlled with NTP), a possiblity that we discount.

Ganged operations possibly consititute the most complex part of Cyclone but the
code weighs in at well under a couple of hundred lines of code. We believe that
this complexity is worth paying to avoid distributed transactions.
